Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-07-04 02_paper/02_study/paper_methods.Rmd
paper method section participants

XXX

# creating a subset to report school type in text
demo.school <- 
  demo.data %>% 
  dplyr::select(Group,
         Percent_schooltype) %>% 
  group_by(Group) %>% 
  summarise_each(funs(sum))

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).

`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% were secondary school teachers.

`r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`). Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.

`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype")`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype")`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype")`% to become special education teachers.

`r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

>>>>

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`). 
`r demo.data %>% filter(Group == "Expert" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the experts were primary school teachers and `r demo.data %>% filter(Group == "Expert" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% were secondary school teachers. `r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`). Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies. 
`r demo.data %>% filter(Group == "Novice" & School_type == "Primary School") %>% pull("Percent_schooltype") %>% unique()`% of the novices were studying to become primary school teachers, `r demo.data %>% filter(Group == "Novice" & School_type == "Secondary School") %>% pull("Percent_schooltype") %>% unique()`% to become secondary school teachers and `r demo.data %>% filter(Group == "Novice" & School_type == "Special Education") %>% pull("Percent_schooltype") %>% unique()`% to become special education teachers. `r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

### 2022-07-04 02_paper/02_study/paper_methods.tex
paper method section participants

The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.80 years (\emph{SD} = 12.30; range: 3-37).

15.80, 15.80, and 15.80\% of the experts were primary school teachers and 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, 84.21, and 84.21\% were secondary school teachers.

47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (17 women; 65.38\%) had a mean age of 23.40 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7.20 semester (\emph{SD} = 2.60; range: 3-11). Furthermore, they had an average teaching experience of 10.90 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.

19.23, 19.23, 19.23, 19.23, and 19.23\% of the novices were studying to become primary school teachers, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, 65.38, and 65.38\% to become secondary school teachers and 15.38, 15.38, 15.38, and 15.38\% to become special education teachers.

88.46\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}. The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.8; Wickham et al., 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson et al., 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham et al., 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.

@@

>>>>

The expert teachers (11 women; 57.89\%) had a mean age of 41.70 years (\emph{SD} = 10.40; range: 27-59) and an average teaching experience of 13.80 years (\emph{SD} = 12.30; range: 3-37).
15.79\% of the experts were primary school teachers and 84.21\% were secondary school teachers. 47\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (17 women; 65.38\%) had a mean age of 23.40 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7.20 semester (\emph{SD} = 2.60; range: 3-11). Furthermore, they had an average teaching experience of 10.90 teaching units à 45min (\emph{SD} = 8.10; range: 0-36) through the internships during their studies.
19.23\% of the novices were studying to become primary school teachers, 65.38\% to become secondary school teachers and 15.38\% to become special education teachers. 88.46\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}. The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.8; Wickham et al., 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson et al., 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham et al., 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-formattable}{}}%
Ren, K., \& Russell, K. (2021). \emph{Formattable: Create 'formattable' data structures}. Retrieved from \url{https://CRAN.R-project.org/package=formattable}
